---
title: "The jpredapir Tutorial: Using jpredapir as a Library"
author: "Andrey Smelter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The jpredapir Tutorial: Using jpredapir as a Library}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `jpredapir` package provides functions to submit, check status, and 
retrieve results from JPred: A Secondary Structure Prediction Server 
([JPred](http://www.compbio.dundee.ac.uk/jpred/)).


## Importing `jpredapir` library

```{r, eval = TRUE}
library(jpredapir)
```

## Print `jpredapir` package help message

```{r, eval = TRUE}
library(jpredapir)
help("jpredapir")
```

## Print `jpredapir` package version

```{r, eval = FALSE}
packageVersion("jpredapir")
```

## Submitting jobs to JPred server

Note that the examples below are **not run**, due to needing access to the server. They do illustrate how to submit jobs
in various formats, however.

There are various example inputs in the `exampledata` directory that accompanies this package. The full list of files can
be found by running the command below on your own installation:

```{r, eval = FALSE}
dir(system.file("exampledata", package = "jpredapir"), full.names = TRUE)
```

These files demonstrate the different types of input that can be used with `jpred`,
and also provide examples that can be used yourself for testing submission
and the returned results.

### Submit a single `raw` sequence

```{r, eval = FALSE}
submit(mode = "single", user_format = "raw", seq = "MQVWPIEGIKKFETLSYLPP")
```

### Submit single sequence in `raw` format using `file` parameter

```{r, eval = FALSE}
submit(mode = "single", user_format = "raw", file = system.file("exampledata/single_raw.example", package = "jpredapir"))
```

Content of `single_raw.example` file:

```{r, echo = FALSE}
cat(scan(system.file("exampledata/single_raw.example", package = "jpredapir"), what = character(), sep = "\n", quiet = TRUE), sep = "\n")
```

### Submit single sequence in `fasta` format using `file` parameter

```{r, eval = FALSE}
submit(mode = "single", user_format = "fasta", file = system.file("exampledata/single_fasta.example", package = "jpredapir"))
```

Content of `single_fasta.example` file:

```{r, echo = FALSE}
cat(scan(system.file("exampledata/single_fasta.example", package = "jpredapir"), what = character(), sep = "\n", quiet = TRUE), sep = "\n")
```

### Submit multiple sequences in `fasta` format using `file` parameter

```{r, eval = FALSE}
submit(mode = "batch", user_format = "fasta", file = system.file("exampledata/batch_fasta.example", package = "jpredapir"), email = "name@domain.com")
```

Content of `batch_fasta.example` file:

```{r, echo = FALSE}
cat(scan(system.file("exampledata/batch_fasta.example", package = "jpredapir"),
  what = character(), sep = "\n", quiet = TRUE), sep = "\n")
```

### Submit multiple sequence alignment files in `fasta` format

```{r, eval = FALSE}
submit(mode = "msa", user_format = "fasta", file = system.file("exampledata/msa_fasta.example", package = "jpredapir"), email = "name@domain.com")
```

Content of `msa_fasta.example` file:

```{r, echo = FALSE}
cat(scan(system.file("exampledata/msa_fasta_short.example", package = "jpredapir"), what = character(),
sep = "\n", quiet = TRUE), sep = "\n")
```

### Submit multiple sequence alignment files in `msf` format

```{r, eval = FALSE}
submit(mode = "msa", user_format = "msf", file = system.file("exampledata/msa_msf.example", package = "jpredapir"), email = "name@domain.com")
```

Content of `msa_msf.example` file:

```{r, echo = FALSE}
cat(scan(system.file("exampledata/msa_msf.example", package = "jpredapir"), what = character(),
sep = "\n", quiet = TRUE), sep = "\n")
```

### Submit multiple sequence alignment files in `blc` format

```{r, eval = FALSE}
submit(mode = "msa", user_format = "blc", file = system.file("exampledata/msa_blc.example", package = "jpredapir"), email = "name@domain.com")
```

Content of `msa_blc.example` file:

```{r, echo = FALSE}
cat(scan(system.file("exampledata/msa_blc_short.example", package = "jpredapir"), what = character(),
sep = "\n", quiet = TRUE), sep = "\n")
```


## Check job status on JPred server

### Check single job status using `jobid`

```{r, eval = FALSE}
status(jobid = "jp_K46D05A")
```

### Check single job status using `jobid` and retrieve results

```{r, eval = FALSE}
status(jobid = "jp_K46D05A", results_dir_path = "jpred_sspred/results")
```

### Check single job status using `jobid`, retrieve results, and decompress archive

```{r, eval = FALSE}
status(jobid = "jp_K46D05A", results_dir_path = "jpred_sspred/results", extract = TRUE)
```

## Retrieve results from JPred server

### Retrieve results using `jobid`

```{r, eval = FALSE}
get_results(jobid = "jp_K46D05A", results_dir_path = "jpred_sspred/results")
```

### Retrieve results using `jobid` and decompress archive

```{r, eval = FALSE}
get_results(jobid = "jp_K46D05A", results_dir_path = "jpred_sspred/results", extract = TRUE)
```


## Check quota

### Check how many jobs you have already submitted on a given day

```{r, eval = FALSE}
quota(email = "name@domain.com")
```

## Check JPred REST interface version

### Check version of JPred REST interface

```{r, eval = FALSE}
check_rest_version()
```
