---
title: "The jpredapir Tutorial: Using jpredapir as a Library"
author: "Andrey Smelter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The jpredapir Tutorial: Using jpredapir as a Library}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `jpredapir` package provides functions to submit, check status, and 
retrieve results from JPred: A Secondary Structure Prediction Server 
([JPred](http://www.compbio.dundee.ac.uk/jpred/)).


## Importing `jpredapir` library

```{r, eval = FALSE}
library(jpredapir)
```

## Print `jpredapir` help message

```{r, eval = FALSE}
help("jpredapir")
```

## Print `jpredapir` package version

```{r, eval = FALSE}
packageVersion("jpredapir")
```

## Submit jobs to JPred server

```{r, eval = FALSE}
submit(mode = "single", user_format = "raw", seq = "MQVWPIEGIKKFETLSYLPP")
```

### Submit single sequence in `raw` format using `file` parameter

```{r, eval = FALSE}
submit(mode = "single", user_format = "raw", file = "inst/exampledata/single_raw.example")
```

Content of `single_raw.example` file:

```
MQVWPIEGIKKFETLSYLPPLTVEDLLKQIEYLLRSKWVPCLEFSKVGFVYRENHRSPGYYDGRYWTMWKLPMFGCTDATQVLKELEEAKKAYPDAFVRIIGFDNVRQVQLISFIAYKPPGC
```

### Submit single sequence in `fasta` format using `file` parameter

```{r, eval = FALSE}
submit(mode = "single", user_format = "fasta", file = "inst/exampledata/single_fasta.example")
```

Content of `single_fasta.example` file:

```
>my test sequence
MQVWPIEGIKKFETLSYLPPLTVEDLLKQIEYLLRSKWVPCLEFSKVGFVYRENHRSPGYYDGRYWTMWKLPMFGCTDATQVLKELEEAKKAYPDAFVRIIGFDNVRQVQLISFIAYKPPGC
```

### Submit multiple sequences in `fasta` format using `file` parameter

```{r, eval = FALSE}
submit(mode = "batch", user_format = "fasta", file = "inst/exampledata/batch_fasta.example", email = "name@domain.com")
```

Content of `batch_fasta.example` file:

```
>my_seq1
MKFLVLLFNILCLFPILGADELVMSPIPTTDVQPKVTFDINSEVSSGPLYLNPVEMAGVK
YLQLQRQPGVQVHKVVEGDIVIWENEEMPLYTCAIVTQNEVPYMAYVELLEDPDLIFFLK
EGDQWAPIPEDQYLARLQQLRQQIHTESFFSLNLSFQHENYKYEMVSSFQHSIKMVVFTP
KNGHICKMVYDKNIRIFKALYNEYVTSVIGFFRGLKLLLLNIFVIDDRGMIGNKYFQLLD
DKYAPISVQGYVATIPKLKDFAEPYHPIILDISDIDYVNFYLGDATYHDPGFKIVPKTPQ
CITKVVDGNEVIYESSNPSVECVYKVTYYDKKNESMLRLDLNHSPPSYTSYYAKREGVWV
TSTYIDLEEKIEELQDHRSTELDVMFMSDKDLNVVPLTNGNLEYFMVTPKPHRDIIIVFD
GSEVLWYYEGLENHLVCTWIYVTEGAPRLVHLRVKDRIPQNTDIYMVKFGEYWVRISKTQ
>my_seq2
MASVKSSSSSSSSSFISLLLLILLVIVLQSQVIECQPQQSCTASLTGLNVCAPFLVPGSP
TASTECCNAVQSINHDCMCNTMRIAAQIPAQCNLPPLSCSAN
>my_seq3
MEKKSIAGLCFLFLVLFVAQEVVVQSEAKTCENLVDTYRGPCFTTGSCDDHCKNKEHLLS
GRCRDDVRCWCTRNC
```

### Submit multiple sequence alignment files in `fasta` format

```{r, eval = FALSE}
submit(mode = "msa", user_format = "fasta", file = "inst/exampledata/msa_fasta.example", email = "name@domain.com")
```

Content of `msa_fasta.example` file:

```
>QUERY_1
MQVWPIEGIKKFETLSYLPPLTVEDLLKQIEYLLRSKWVPCLEFSKVGFVYRENHRSPGYYDGRYWTMWKLP
MFGCTDATQVLKELEEAKKAYPDAFVRIIGFDNVRQVQLISFIAYKPPGC
>UniRef90_Q40250_2
MKVWPPIGLKKYETLSYLPPLSDEALSKEIDYLIRNKWIPCLEFEEHGFVYREHHHSPGYYDGRYWTMWKLP
MFGCTDSAQVMKEVGECKKEYPNAFIRVIGFDNIRQVQCISFIVAKPPGV
>UniRef90_A7YVW5_3
MQVWPPLGKRKFETLSYLPPLPVDALLKQIDYLIRSGWIPCIEFTVEGFVYREHHHSPGYYDGRYWTMWKLP
MYGCTDSTQVLAEVEANKKEYPNSYIRIIGFDNKRQVQCVSFIVHTPPS-
>UniRef90_P04714_4
MQVWPPYGKKKYETLSYLPDLTDEQLLKEIEYLLNKGWVPCLEFTEHGFVYREYHASPRYYDGRYWTMWKLP
MFGCTDATQVLGELQEAKKAYPNAWIRIIGFDNVRQVQCISFIAYKPPG-
>UniRef90_W9RUU9_5
MQVWPPRGKLKFETLSYLPDLTDEQLLKEIDYLLRSNWIPCLEFEVKAHIYRENNRSPGYYDGRYWTMWKLP
MFGCTDATQVLAEVQETKKAYPDAHVRIIGFDNNRQVQCISFIAYKPPA-
```

### Submit multiple sequence alignment files in `msf` format

```{r, eval = FALSE}
submit(mode = "msa", user_format = "msf", file = "inst/exampledata/msa_msf.example", email = "name@domain.com")
```

Content of `msa_msf.example` file:

```

 /tmp/filelPdICy  MSF: 108  Type: N  January 01, 1776  12:00  Check: 2741 ..

 Name: 0_1a             Len:   108  Check:  4063  Weight:  1.00
 Name: 1_MA             Len:   108  Check:  4875  Weight:  1.00
 Name: 2_KE             Len:   108  Check:   449  Weight:  1.00
 Name: 3_NC             Len:   108  Check:  3354  Weight:  1.00

//

           0_1a  APAFSVSPAS GASDGQSVSV SVAAAGETYY IAQCAPVGGQ DACNPATATS
           1_MA  APGVTVTPAT GLSNGQTVTV SATTPGTVYH VGQCAVVEGV IGCDATTSTD
           2_KE  SAAVSVSPAT GLADGATVTV SASATSTSAT ALQCAILAGR GACNVAEFHD
           3_NC  APTATVTPSS GLSDGTVVKV AGAQAGTAYD VGQCAWVDGV LACNPADFSS

           0_1a  FTTDASGAAS FSFTVRKSYA GQTPSGTPVG SVDCATDACN LGAGNSGLNL
           1_MA  VTADAAGKIT AQLKVHSSFQ AVVANGTPWG TVNCKVVSCS AGLGSDSGEG
           2_KE  FSLSG.GEGT TSVVVRRSFT GYVPDGPEVG AVDCDTAPCE IVVGGNTGEY
           3_NC  VTADANGSAS TSLTVRRSFE GFLFDGTRWG TVDCTTAACQ VGLSDAAGNG

           0_1a  GHVALTFG
           1_MA  AAQAITFA
           2_KE  GNAAISFG
           3_NC  PGVAISFN
```

### Submit multiple sequence alignment files in `blc` format

```{r, eval = FALSE}
submit(mode = "msa", user_format = "blc", file = "inst/exampledata/msa_blc.example", email = "name@domain.com")
```

Content of `msa_blc.example` file:

```
>0_1a  Name
>1_MA  Name
>2_KE  Name
>3_NC  Name
* iteration 1
AASA
PPAP
AGAT
FVVA
STST
VVVV
STST
PPPP
AAAS
*
```

## Check job status on JPred server

### Check single job status using `jobid`

```{r, eval = FALSE}
status(jobid = "jp_K46D05A")
```

### Check single job status using `jobid` and retrieve results

```{r, eval = FALSE}
status(jobid = "jp_K46D05A", results_dir_path = "jpred_sspred/results")
```

### Check single job status using `jobid`, retrieve results, and decompress archive

```{r, eval = FALSE}
status(jobid = "jp_K46D05A", results_dir_path = "jpred_sspred/results", extract = TRUE)
```

## Retrieve results from JPred server

### Retrieve results using `jobid`

```{r, eval = FALSE}
get_results(jobid = "jp_K46D05A", results_dir_path = "jpred_sspred/results")
```

### Retrieve results using `jobid` and decompress archive

```{r, eval = FALSE}
get_results(jobid = "jp_K46D05A", results_dir_path = "jpred_sspred/results", extract = TRUE)
```


## Check quota

### Check how many jobs you have already submitted on a given day

```{r, eval = FALSE}
quota(email = "name@domain.com")
```

## Check JPred REST interface version

### Check version of JPred REST interface

```{r, eval = FALSE}
check_rest_version()
```
