---
title: "The jpredapir Tutorial: Using jpredapir Command Line Interface"
author: "Andrey Smelter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The jpredapir Tutorial: Using jpredapir Command Line Interface}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `jpredapir` package provides functions to submit, check status, and 
retrieve results from JPred: A Secondary Structure Prediction Server 
([JPred](http://www.compbio.dundee.ac.uk/jpred/)).

## Command Line Interface

```
jpredapir command-line interface

The JPred API allows users to submit jobs from the command-line.

Usage:
    jpredapi.R submit (--mode=<mode> --format=<format>) (--file=<filename> | --seq=<sequence>) [--email=<name@domain.com>] [--name=<name>] [--rest=<address>] [--skipPDB] [--silent]
    jpredapi.R status (--jobid=<id>) [--results=<path>] [--wait=<interval>] [--attempts=<max>] [--rest=<address>] [--jpred4=<address>] [--extract] [--silent]
    jpredapi.R get_results (--jobid=<id>) [--results=<path>] [--wait=<interval>] [--attempts=<max>] [--rest=<address>] [--jpred4=<address>] [--extract] [--silent]
    jpredapi.R quota (--email=<name@domain.com>) [--silent]
    jpredapi.R check_rest_version [--rest=<address>] [--silent]
    jpredapi.R -h | --help
    jpredapi.R -v | --version

Options:
    -h, --help                 Show this help message.
    -v, --version              Show jpredapir package version.
    --silent                   Do not print messages.
    --extract                  Extract results tar.gz archive.
    --skipPDB                  PDB check.
    --mode=<mode>              Submission mode, possible values: single, batch, msa.
    --format=<format>          Submission format, possible values: raw, fasta, msf, blc.
    --file=<filename>          Filename of a file with the job input (sequence(s)).
    --seq=<sequence>           Instead of passing input file, for single-sequence submission.
    --email=<name@domain.com>  E-mail address where job report will be sent (optional for all but batch submissions).
    --name=<name>              Job name.
    --jobid=<id>               Job id.
    --results=<path>           Path to directory where to save archive with results.
    --rest=<address>           REST address of server [default: http://www.compbio.dundee.ac.uk/jpred4/cgi-bin/rest].
    --jpred4=<address>         Address of Jpred4 server [default: http://www.compbio.dundee.ac.uk/jpred4].
    --wait=<interval>          Wait interval before retrying to check job status in seconds [default: 60].
    --attempts=<max>           Maximum number of attempts to check job status [default: 10].
```

## Find `jpredapir` CLI executable

To find `jpredapi.R` executable start your `R` shell and type:

```{r, eval = FALSE}
shQuote(system.file("exec", "jpredapi.R", package = "jpredapir"))
```

Output:

```
'path/to/jpredapir/exec/jpredapi.R'
```

## Print `jpredapir` help message

```{r, engine = 'bash', eval = FALSE}
$ Rscript jpredapir/exec/jpredapi.R --help
```

## Print `jpredapir` package version

```{r, engine = 'bash', eval = FALSE}
$ Rscript jpredapir/exec/jpredapi.R --version
```

## Submit jobs to JPred server

### Submit single sequence in `raw` format using `--seq` parameter

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R submit --mode=single --format=raw --seq=MQVWPIEGIKKFETLSYLPP
```

### Submit single sequence in `raw` format using `--file` parameter

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R submit --mode=single --format=raw --file=inst/exampledata/single_raw.example
```

Content of `single_raw.example` file:

```
MQVWPIEGIKKFETLSYLPPLTVEDLLKQIEYLLRSKWVPCLEFSKVGFVYRENHRSPGYYDGRYWTMWKLPMFGCTDATQVLKELEEAKKAYPDAFVRIIGFDNVRQVQLISFIAYKPPGC
```

### Submit single sequence in `fasta` format using `--file` parameter

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R submit --mode=single --format=fasta --file=inst/exampledata/single_fasta.example
```

Content of `single_fasta.example` file:

```
>my test sequence
MQVWPIEGIKKFETLSYLPPLTVEDLLKQIEYLLRSKWVPCLEFSKVGFVYRENHRSPGYYDGRYWTMWKLPMFGCTDATQVLKELEEAKKAYPDAFVRIIGFDNVRQVQLISFIAYKPPGC
```

### Submit multiple sequences in `fasta` format using `--file` parameter

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R submit --mode=batch --format=fasta --file=inst/exampledata/batch_fasta.example --email=name@domain.com
```

Content of `batch_fasta.example` file:

```
>my_seq1
MKFLVLLFNILCLFPILGADELVMSPIPTTDVQPKVTFDINSEVSSGPLYLNPVEMAGVK
YLQLQRQPGVQVHKVVEGDIVIWENEEMPLYTCAIVTQNEVPYMAYVELLEDPDLIFFLK
EGDQWAPIPEDQYLARLQQLRQQIHTESFFSLNLSFQHENYKYEMVSSFQHSIKMVVFTP
KNGHICKMVYDKNIRIFKALYNEYVTSVIGFFRGLKLLLLNIFVIDDRGMIGNKYFQLLD
DKYAPISVQGYVATIPKLKDFAEPYHPIILDISDIDYVNFYLGDATYHDPGFKIVPKTPQ
CITKVVDGNEVIYESSNPSVECVYKVTYYDKKNESMLRLDLNHSPPSYTSYYAKREGVWV
TSTYIDLEEKIEELQDHRSTELDVMFMSDKDLNVVPLTNGNLEYFMVTPKPHRDIIIVFD
GSEVLWYYEGLENHLVCTWIYVTEGAPRLVHLRVKDRIPQNTDIYMVKFGEYWVRISKTQ
>my_seq2
MASVKSSSSSSSSSFISLLLLILLVIVLQSQVIECQPQQSCTASLTGLNVCAPFLVPGSP
TASTECCNAVQSINHDCMCNTMRIAAQIPAQCNLPPLSCSAN
>my_seq3
MEKKSIAGLCFLFLVLFVAQEVVVQSEAKTCENLVDTYRGPCFTTGSCDDHCKNKEHLLS
GRCRDDVRCWCTRNC
```

### Submit multiple sequence alignment files in `fasta` format

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R submit --mode=msa --format=fasta --file=inst/exampledata/msa_fasta.example --email=name@domain.com
```

Content of `msa_fasta.example` file:

```
>QUERY_1
MQVWPIEGIKKFETLSYLPPLTVEDLLKQIEYLLRSKWVPCLEFSKVGFVYRENHRSPGYYDGRYWTMWKLP
MFGCTDATQVLKELEEAKKAYPDAFVRIIGFDNVRQVQLISFIAYKPPGC
>UniRef90_Q40250_2
MKVWPPIGLKKYETLSYLPPLSDEALSKEIDYLIRNKWIPCLEFEEHGFVYREHHHSPGYYDGRYWTMWKLP
MFGCTDSAQVMKEVGECKKEYPNAFIRVIGFDNIRQVQCISFIVAKPPGV
>UniRef90_A7YVW5_3
MQVWPPLGKRKFETLSYLPPLPVDALLKQIDYLIRSGWIPCIEFTVEGFVYREHHHSPGYYDGRYWTMWKLP
MYGCTDSTQVLAEVEANKKEYPNSYIRIIGFDNKRQVQCVSFIVHTPPS-
>UniRef90_P04714_4
MQVWPPYGKKKYETLSYLPDLTDEQLLKEIEYLLNKGWVPCLEFTEHGFVYREYHASPRYYDGRYWTMWKLP
MFGCTDATQVLGELQEAKKAYPNAWIRIIGFDNVRQVQCISFIAYKPPG-
>UniRef90_W9RUU9_5
MQVWPPRGKLKFETLSYLPDLTDEQLLKEIDYLLRSNWIPCLEFEVKAHIYRENNRSPGYYDGRYWTMWKLP
MFGCTDATQVLAEVQETKKAYPDAHVRIIGFDNNRQVQCISFIAYKPPA-
```

### Submit multiple sequence alignment files in `msf` format

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R submit --mode=msa --format=msf --file=inst/exampledata/msa_msf.example --email=name@domain.com
```

Content of `msa_msf.example` file:

```

 /tmp/filelPdICy  MSF: 108  Type: N  January 01, 1776  12:00  Check: 2741 ..

 Name: 0_1a             Len:   108  Check:  4063  Weight:  1.00
 Name: 1_MA             Len:   108  Check:  4875  Weight:  1.00
 Name: 2_KE             Len:   108  Check:   449  Weight:  1.00
 Name: 3_NC             Len:   108  Check:  3354  Weight:  1.00

//

           0_1a  APAFSVSPAS GASDGQSVSV SVAAAGETYY IAQCAPVGGQ DACNPATATS
           1_MA  APGVTVTPAT GLSNGQTVTV SATTPGTVYH VGQCAVVEGV IGCDATTSTD
           2_KE  SAAVSVSPAT GLADGATVTV SASATSTSAT ALQCAILAGR GACNVAEFHD
           3_NC  APTATVTPSS GLSDGTVVKV AGAQAGTAYD VGQCAWVDGV LACNPADFSS

           0_1a  FTTDASGAAS FSFTVRKSYA GQTPSGTPVG SVDCATDACN LGAGNSGLNL
           1_MA  VTADAAGKIT AQLKVHSSFQ AVVANGTPWG TVNCKVVSCS AGLGSDSGEG
           2_KE  FSLSG.GEGT TSVVVRRSFT GYVPDGPEVG AVDCDTAPCE IVVGGNTGEY
           3_NC  VTADANGSAS TSLTVRRSFE GFLFDGTRWG TVDCTTAACQ VGLSDAAGNG

           0_1a  GHVALTFG
           1_MA  AAQAITFA
           2_KE  GNAAISFG
           3_NC  PGVAISFN
```

### Submit multiple sequence alignment files in `blc` format

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R submit --mode=msa --format=blc --file=inst/exampledata/msa_blc.example --email=name@domain.com
```

Content of `msa_blc.example` file:

```
>0_1a  Name
>1_MA  Name
>2_KE  Name
>3_NC  Name
* iteration 1
AASA
PPAP
AGAT
FVVA
STST
VVVV
STST
PPPP
AAAS
*
```

## Check job status on JPred server

### Check single job status using `jobid`

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R status --jobid=jp_K46D05A
```

### Check single job status using `jobid` and retrieve results

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R status --jobid=jp_K46D05A --results=jpred_sspred/results
```

### Check single job status using `jobid`, retrieve results, and decompress archive

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R status --jobid=jp_K46D05A --results=jpred_sspred/results --extract
```

## Retrieve results from JPred server

### Retrieve results using `jobid`

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R get_results --jobid=jp_K46D05A --results=jpred_sspred/results
```

### Retrieve results using `jobid` and decompress archive

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R get_results --jobid=jp_K46D05A --results=jpred_sspred/results --extract
```

## Check quota

### Check how many jobs you have already submitted on a given day

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R quota --email=name@domain.com
```

## Check JPred REST interface version

### Check version of JPred REST interface

```{r, engine = 'bash', eval = FALSE}
Rscript jpredapir/exec/jpredapi.R check_rest_version
```

